---
title: "My favorite R packages in 2022"
author: "Pedro Nascimento de Lima"
date: 2022-12-01T21:13:14-05:00
categories: ["R"]
tags: ["R Packages", "R", "programming"]
description: "Some R packages are so useful that knowing them and not sharing is a sin."
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# It's 2022, and R still rocks

It is no secret to close friends that I am a big fan of the `R` ecosystem. R is great, not necessarily as a language, but as a community.

I've used R for almost 10 years now, and the R community continues to crank out a serious amount of utility-maximizing tools for its users. Here are some of the packages that I've started to use recently.

## `showtext`

if you are using `ggplot` and you don't use `showtext`, *you are missing out*. Ever wanted to use some non-standard fonts, but struggled? Look no further for pixel-perfect figures.

For example, I use showtext with the `randplot` R package to create some cute figures.

```{r}
library(showtext)
```


## `ggdensity`

Have you ever had to present results of multivariate distributions (i.e., prediction intervals) and used ggplot's `geom_density`? Well, 2-dimensional density functions are not very interpretable, particularly by human beings. 

Instead, use highest-density regions (HDR) plots, and tell your audience "95% of those points are in that region, and any point in that region is more likely than any point outside of it".
